Supplementary Information for RVD2: An ultra-sensitive variant detection model for low-depth heterogeneous next-generation sequencing data

### 2014-05-02 doc/bioinformatics2014/revision0/supplementary_info.tex

\begin{figure}[!bpth]
    \centering
    \subfloat[\label{fig:brca_MAF:a}]{{\includegraphics[width=0.2\textwidth]{pdf_figs/RVD2_model.pdf} }}%
    \quad
    \quad
    \subfloat[ \label{fig:brca_MAF:b}]{{\includegraphics[width=0.7\textwidth]{pdf_figs/GMexample.pdf} }}%
    \caption{(A) RVD2 Graphical Model. (B) Example to illustrate the proposal graphical model and generative process. Here we want to generate a simulation sample with 3 replicates, and each replicate is a 5bp long sequence. Therefore, we have $ J = 5 $, $N = 3$. The hyperparameters in orange, $\mu_0 \in \RR^{1 \times 1}$, $M_0 \in \RR^{1 \times 1}$, $M \in \RR^{5 \times 1}$ are set. $n \in \RR^{5 \times 3}$ in the generative process is given as well. The generative process is: (1) Sample the local error rate $\mu \in \RR^{5 \times 1}$ by drawing random numbers $\mu_j \thicksim \text{Beta}(\mu_0, M_0)$. (2) Use $\mu $ and $ M $ to sample $\theta \in \RR^{5 \times 3}$ by drawing random samples $\theta_{ji} \thicksim \text{Beta}(\mu_j, M_j)$. (3) Use $\theta \in \RR^{5 \times 3}$ and $n \in \RR^{5 \times 3}$ to sample $r \in \RR^{5 \times 3}$ by drawing random numbers $r_{ji} \thicksim \text{Binomial}(\theta_{ji}, n_{ji})$.} 
    \label{fig:brca_MAF}%
\end{figure}

>>>>

\begin{figure}[!bpth]
    \centering
    \subfloat[\label{fig:example:a}]{{\includegraphics[width=0.2\textwidth]{pdf_figs/RVD2_model.pdf} }}%
    \quad
    \quad
    \subfloat[ \label{fig:example:b}]{{\includegraphics[width=0.7\textwidth]{pdf_figs/GMexample.pdf} }}%
    \caption{(A) RVD2 Graphical Model. (B) Example to illustrate the proposal graphical model and generative process. Here we want to generate a simulation sample with 3 replicates, and each replicate is a 5bp long sequence. Therefore, we have $ J = 5 $, $N = 3$. The hyperparameters in orange, $\mu_0 \in \RR^{1 \times 1}$, $M_0 \in \RR^{1 \times 1}$, $M \in \RR^{5 \times 1}$ are set. $n \in \RR^{5 \times 3}$ in the generative process is given as well. The generative process is: (1) Sample the local error rate $\mu \in \RR^{5 \times 1}$ by drawing random numbers $\mu_j \thicksim \text{Beta}(\mu_0, M_0)$. (2) Use $\mu $ and $ M $ to sample $\theta \in \RR^{5 \times 3}$ by drawing random samples $\theta_{ji} \thicksim \text{Beta}(\mu_j, M_j)$. (3) Use $\theta \in \RR^{5 \times 3}$ and $n \in \RR^{5 \times 3}$ to sample $r \in \RR^{5 \times 3}$ by drawing random numbers $r_{ji} \thicksim \text{Binomial}(\theta_{ji}, n_{ji})$.} 
    \label{fig:example}
\end{figure}
